---
title: "Demo of RregressPkg::plot_replace_missing()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(mlbench)
library(dplyr)
library(RregressPkg)
library(RplotterPkg)
```


## Simple example

1. Create the data.frame with NA's and NaN's and other values considered missing:
```{r}
set.seed(5648)
df <- data.frame(
  x = 1:20,
  y = LETTERS[1:20],
  z = rnorm(20, mean = 10, sd = 2.1)
)
df$x[1:2] <- NA
df$x[[5]] <- 9999
df$x[[8]] <- 1111
df$x[12:15] <- NaN
df$z[8:9] <- NaN
df$z[18:19] <- NA
```

2. Show the counts of missing values:
```{r}
missing_lst <- RregressPkg::plot_replace_missing(
  df = df,
  variables = c("x", "z"),
  miss_values = c(1111, 9999),
  title = "Counts of Missing Values"
)
missing_lst$missing_plot
```

3. Replace missing values with the mean value for the variable:
```{r}
missing_lst <- RregressPkg::plot_replace_missing(
  df = df,
  variables = c("x", "z"),
  miss_values = c(1111, 9999),
  replace_fun = "median"
)
colnames(missing_lst$replacement_df) <- c("new_x", "new_y", "new_z")
df_all <- cbind(df, missing_lst$replacement_df)

RplotterPkg::create_table(
  x = df_all, 
  caption = "Missing Replaced With Median Values",
  scroll_height = "250px",
  fixed_thead = T)
```

4. Replace missing values using "next observation carried backward":
```{r}
missing_lst <- RregressPkg::plot_replace_missing(
  df = df,
  variables = c("x", "z"),
  miss_values = c(1111, 9999),
  replace_fun = "nocb"
)

colnames(missing_lst$replacement_df) <- c("new_x", "new_y", "new_z")
df_all <- cbind(df, missing_lst$replacement_df)

RplotterPkg::create_table(
  x = df_all, 
  caption = "Missing Replaced With 'nocb' Values",
  scroll_height = "250px",
  fixed_thead = T)
```

## Soybean example

1. Set up the data:

There are 683 observations and 36 variables.  The class of the measurement variables in Soybean is either "factor" or "ordered".  We will ignore the first variable *Class* since it is character type and convert all others to numeric.
```{r}
data("Soybean", package = "mlbench")
for(i in 2:ncol(Soybean)){
  Soybean[,i] <- as.numeric(Soybean[,i])
}
```

2. Set the columns of interest and insert some missing values. 
 *date* variable has one missing value. For testing assign 2 missing values to *date* variable for a total of 3.
 *leaves* variable has no missing values. For testing assign 5 missing values to the *leaves* variable for a total of 5.
```{r}
columns_of_interest <- colnames(Soybean)[2:ncol(Soybean)]

Soybean$date[[3]] <- NA
Soybean$date[[4]] <- 99
Soybean$leaves[[4]] <-  NA
Soybean$leaves[[5]] <-  "N/A"
Soybean$leaves[[6]] <-  "na"
Soybean$leaves[[7]] <- NA
Soybean$leaves[[8]] <- NaN
```
 
3. Get a count of the missing values:
```{r}
soybean_missing_lst <- RregressPkg::plot_replace_missing(
  df = Soybean,
  variables = columns_of_interest,
  miss_values = c("N/A", "na", 99),
  title = "Count of Missing Values",
  subtitle = "mlbench::Soybean data set",
  x_title = "Variable",
  y_title = "Count of Missing Values",
  bar_size = 0.6,
  bar_color = "white",
  bar_labels = TRUE,
  bar_label_size = 3,
  do_coord_flip = TRUE,
  order_bars = "asc"
)
soybean_missing_lst$missing_plot
```

4. Apply a user defined function for replacing missing values:
```{r}
missing_val_fun <- function(x){
  xx <- as.numeric(x)
  return((max(xx) - min(xx))/2)
}
soybean_missing_lst <- RregressPkg::plot_replace_missing(
  df = Soybean,
  variables = columns_of_interest,
  replace_fun = missing_val_fun,
  miss_values = c("N/A", "na", 99),
  title = "Count of Missing Values",
  subtitle = "mlbench::Soybean data set",
  x_title = "Variable",
  y_title = "Count of Missing Values",
  bar_size = 0.6,
  bar_color = "white",
  bar_labels = TRUE,
  bar_label_size = 3,
  do_coord_flip = TRUE,
  order_bars = "asc"
)
soybean_missing_lst$replacement_df %>% 
  select(date, leaves) %>% 
  head(n = 10)
```
Note that *date* variable now has a value 3 and *leaves* variable now has a value of 0.5 for their missing values.

5. Run `RregressPkg::plot_replace_missing()` on the replacement data.frame to check on missing values:
```{r}
soybean_missing_lst <- RregressPkg::plot_replace_missing(
  df = soybean_missing_lst$replacement_df,
  variables = columns_of_interest,
  miss_values = c("N/A", "na", 99),
  title = "Count of Missing Values",
  subtitle = "mlbench::Soybean data set",
  x_title = "Variable",
  y_title = "Count of Missing Values",
  bar_size = 0.6,
  bar_color = "white",
  bar_labels = TRUE,
  bar_label_size = 3,
  do_coord_flip = TRUE,
  order_bars = "asc",
  y_major_breaks = c(0,1,2)
)
soybean_missing_lst$missing_plot
```

