---
title: "Demo for RregressPkg::ols_F_LM_calc()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
```

## Predicting baseball salaries and alternative OLS models
Source: "Using R for Introductory Econometrics" by Florian Heiss, Section 4.3 page 109
 
Also: "Introductory Econometrics, A Modern Approach, 6th edition" by Jeffery Wooldridge, Section 4.5 page 127

Unrestricted OLS Formula: log(salary) ~ years + gamesyr + bavg + hrunsyr + rbisyr

Restricted OLS Formula: log(salary) ~ years + gamesyr

Null hypothesis: 

$$H_{0}: \beta_{bavg} = \beta_{hrunsyr} = \beta_{rbisyr} = 0$$
Alternative hypothesis: at least one of $\beta_{years}$ or $\beta{gamesyr}$ has an influence on *salary*.

### Set up the data
```{r}
data("mlb1", package = "wooldridge")
mlb1_dt <- data.table::setDT(mlb1)
mlb1_dt <- mlb1_dt[,.(salary, years, gamesyr, bavg, hrunsyr, rbisyr)]
```

### Define the unrestricted/restricted OLS models
```{r}
ur_formula_obj <- log(salary) ~ years + gamesyr + bavg + hrunsyr + rbisyr
r_formula_obj <- log(salary) ~ years + gamesyr
```

### Run `RregressPkg::ols_F_LM_calc()`
```{r}
F_LM_lst <- RregressPkg::ols_F_LM_calc(
  df = mlb1,
  ur_formula_obj = ur_formula_obj,
  r_formula_obj = r_formula_obj,
  confid_level = 0.99
)
```

### Show the F-LM statistics
```{r}
RplotterPkg::create_table(
  x = F_LM_lst$F_LM_df,
  caption = "Reject bavg = hrunsyr = rbisyr = 0 at 99% confidence level",
  full_width = T,
  align_v = rep("c",4)
)
```

## Economic Model of Crime
Source: "Using R for Introductory Econometrics" by Florian Heiss, Section 5.2 page 121
 
Also: "Introductory Econometrics, A Modern Approach, 6th edition" by Jeffery Wooldridge, Section 5.2a page 158

Unrestricted OLS Formula: narr86 ~ pcnv + avgsen + tottime + ptime86 + qemp86 

Restricted OLS Formula: narr86 ~ pcnv + ptime86 + qemp86

Null hypothesis: 

$$H_{0}: \beta_{avgsen} = \beta_{tottime} = 0$$

### Set up the data
```{r}
data("crime1", package = "wooldridge")
crime1_dt <- data.table::setDT(crime1)
crime1_dt <- crime1_dt[, .(narr86, pcnv, avgsen, tottime, ptime86, qemp86)]
```

### Define the unrestricted/restricted OLS models
```{r}
ur_formula_obj <- narr86 ~ pcnv + avgsen + tottime + ptime86 + qemp86 
r_formula_obj <- narr86 ~ pcnv + ptime86 + qemp86 
```

### Run `RregressPkg::ols_F_LM_calc()`
```{r}
F_LM_lst <- RregressPkg::ols_F_LM_calc(
  df = crime1_dt,
  ur_formula_obj = ur_formula_obj,
  r_formula_obj = r_formula_obj,
  confid_level = 0.90
)
```

### Show the F-LM statistics
```{r}
RplotterPkg::create_table(
  x = F_LM_lst$F_LM_df,
  caption = "Do not reject avgsen = tottime = 0 at 90% confidence level",
  full_width = T,
  align_v = rep("c", 4)
)
```

