---
title: "Demo of RregressPkg::plot_correlations()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

<div>Author: Rick Dean</div>
<div>Article date: `r params$date`</div>

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(data.table)
library(here)
library(ggplot2)
library(RplotterPkg)
library(RregressPkg)
```

## Correlations among selected variables in `ggplot2::midwest`
1. Create a data frame with 12 selected variables and 437 observations:
```{r}
midwest_dt <- data.table::setDT(ggplot2::midwest)
midwest_dt <- midwest_dt[, .(popdensity, percwhite, percblack, popadults, perchsd, percollege, percprof,
                             percbelowpoverty, percchildbelowpovert, percadultpoverty, percelderlypoverty, inmetro)]
```

2. Plot the correlations without clustering, accepting all the plot defaults:
```{r, fig.width=13, fig.height=13}
corr_lst <- RregressPkg::plot_correlations(
  x = midwest_dt,
  title = "Correlations of Midwest Demographic Variables",
  subtitle = "Source: ggplot2::midwest"
)
corr_lst$corr_plot
```

3. Repeat the above plot with clustering:
```{r, fig.width=13, fig.height=13}
corr_lst <- RregressPkg::plot_correlations(
  x = midwest_dt,
  title = "Cluster Correlations of Midwest Demographic Variables",
  subtitle = "Source: ggplot2::midwest",
  cluster_corr = TRUE
)
corr_lst$corr_plot
```

## Correlations related to blood pressure

Source: PennState Stat 501 Eberly College of Science, Section 12.1, Example 12.1

1. Read the data:
```{r}
current_dir <- here::here()
data_dir <- file.path(current_dir, "demos/data")
data_path <- file.path(data_dir, "bloodpress.txt")
bloodpress_dt <- data.table::fread(data_path)
bloodpress_dt <- bloodpress_dt[, !c("Pt")]
```

2. Compute and show the correlations among the variables:
```{r}
bp_corr_lst <- RregressPkg::plot_correlations(
  x = bloodpress_dt,
  title = "Blood Pressure Related Variables",
  subtitle = "PennState Stat 501 Eberly College of Science"
)
row_names_df <- data.frame(
  Variable = row.names(bp_corr_lst$corr)
) 
df <- cbind(row_names_df, as.data.frame(bp_corr_lst$corr))
RplotterPkg::create_table(
  x = df,
  caption = "Blood Pressure Correlations"
)

```

