---
title: "Demo of RregressPkg::plot_pca()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

<div>Author: Rick Dean</div>
<div>Article date: `r params$date`</div>

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(here)
library(RregressPkg)
library(RplotterPkg)
library(dplyr)
library(ggrepel)
library(ggplot2)
library(grid)

current_dir <- here::here()
```

## Principal Components of pilots

Data Reference: Travers, R. M. W. (1939), “The Use of a Discriminant Function in the Treatment of Psychological Group Differences,” Psychometrika, 4 (1), 25–32.

R scripts inspired by [Principal Component Analysis with R Example](https://aaronschlegel.me/principal-component-analysis-r-example.html)

1. Read in the data:
```{r}
data_path <- file.path(current_dir, "demos/data/pilot.data")
pilots <- utils::read.table(data_path, sep = "")
measurements <- c("Intelligence", "Form Relations", "Dynamometer", "Dotting", "Coordination", "Perservation")
colnames(pilots) <- c("Group", measurements)
```

2. Create a data frame of measurements and pilot groups:
```{r}
pilots_df <- as.data.frame(pilots[2:7])
pilots_df <- pilots_df %>%
  mutate(Group = ifelse(pilots$Group == 1, "Apprentice", "Pilot"))
```

3. Call `RregressPkg::plot_pca()` with scaling of the raw measurements:
```{r, fig.width=13, fig.height=13}
pilots_pca_plots <- RregressPkg::plot_pca(
  df = pilots_df,
  measures = measurements,
  center = T,
  scale. = T,
  rank. = 4,
  aes_fill = "Group",
  pts_size = 2,
  palette_colors = c("red","blue"),
  x_limits = c(-4, 2),
  x_major_breaks = seq(-4, 2, 1),
  title = "Principal Components of Pilots and Apprentices",
  subtitle = "6 tested attributes from 20 pilots and 20 apprentices",
  figure_width = 12
)
```

4. Plot the percentage of explained variance by the components (Scree plot):
```{r}
plot_df <- data.frame(
  component = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6"),
  variance = pilots_pca_plots$percent_var
)
RplotterPkg::create_bar_plot(
  df = plot_df,
  aes_x = "component",
  aes_y = "variance",
  title = "Principal Components of Pilot Traits",
  subtitle = "Component's percent of explained variance",
  x_title = "Component",
  y_title = "Percent of Explained Variance",
  rot_y_tic_label = T,
  bar_fill = "blue"
)
```

## Principal Components of wine

Data Reference: [Wine Data Set](https://archive.ics.uci.edu/ml/datasets/Wine)

R script inspired by [Principal Component Analysis in R, R-Bloggers](https://www.r-bloggers.com/2017/01/principal-component-analysis-in-r/)

1. Read in the data:
```{r}
data_path <- file.path(current_dir, "demos/data/wine.data")
wine_df <- read.table(data_path, sep = ",")
```

2. 2. Create a data frame of measurements and *Class* groups:
```{r}
measurements <- c("Alcohol","Malic acid","Ash","Alcalinity of ash",
                  "Magnesium", "Total phenols", "Flavanoids", "Nonflavanoid phenols",
                  "Proanthocyanins", "Color intensity", "Hue", "OD280/OD315 of diluted wines", "Proline")
colnames(wine_df) <- c("Class",measurements)

wine_df <- wine_df %>%
  mutate(Class = as.factor(wine_df$Class))
```

3. Call `RregressPkg::plot_pca()` with scaling of the raw measurements:
```{r, fig.width=13, fig.height=13}
wine_pca_plots <- RregressPkg::plot_pca(
  df = wine_df,
  center = T,
  scale. = T,
  rank. = 5,
  measures = measurements,
  aes_fill = "Class",
  pts_size = 2,
  palette_colors = c("red","blue","green"),
  x_limits = c(-5, 5),
  x_major_breaks = seq(-5, 5, 1),
  y_limits = c(-5,5),
  y_major_breaks = seq(-5,5,1),
  title = "Principal Components of Wine",
  subtitle = "13 attributes from 178 samples of 3 classes",
  figure_width = 12
)
```

4. Plot the percentage of explained variance by the components (Scree plot):
```{r}
plot_df <- data.frame(
  component = c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6", "PC7", "PC8", "PC9", "PC10", "PC11", "PC12", "PC13"),
  variance = wine_pca_plots$percent_var
)
RplotterPkg::create_bar_plot(
  df = plot_df,
  aes_x = "component",
  aes_y = "variance",
  title = "Principal Components of Wine Traits",
  subtitle = "Component's percent of explained variance",
  x_title = "Component",
  y_title = "Percent of Explained Variance",
  rot_y_tic_label = T,
  bar_fill = "blue",
  order_bars = "desc"
)
```
