---
title: "Demo of RregressPkg::low_predictor_collinearity()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

<div>Author: Rick Dean</div>
<div>Article date: `r params$date`</div>

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(here)
library(RregressPkg)
```

## Potential predictors of blood pressure

The data set of predictors originates from [PennState Eberly College of Science](https://online.stat.psu.edu/stat501/lesson/welcome-stat-501) Lesson 12: Multicollinearity & Other Regression Pitfalls.

1. Read in the data set:
```{r}
current_dir <- here::here()
data_dir <- file.path(current_dir, "demos/data")
data_path <- file.path(data_dir, "bloodpress.txt")
bloodpress_dt <- data.table::fread(data_path)
bloodpress_dt <- bloodpress_dt[, !c("Pt")]
```


2. Show the correlations among the predictors and the blood pressure response variable:
```{r}
bp_corr_lst <- RregressPkg::plot_correlations(
  x = bloodpress_dt,
  title = "Blood Pressure Related Variables",
  subtitle = "PennState Stat 501 Eberly College of Science"
)
row_names_df <- data.frame(
  Variable = row.names(bp_corr_lst$corr)
) 
df <- cbind(row_names_df, as.data.frame(bp_corr_lst$corr))
RplotterPkg::create_table(
  x = df,
  caption = "Blood Pressure Correlations"
)
```

Note the high correlation between *Weight* and *BSA* at .88. Also *Weight* and *Pulse* have a correlation of .66

3. Call `RregressPkg::low_predictor_collinarity()` with the data frame of predictors:
Using the default of .75 for the threshold correlation.
```{r}
bloodpress_predictors_dt <- bloodpress_dt[, !c("BP")]
low_collinearity_lst <- RregressPkg::low_predictor_collinearity(
  df = bloodpress_predictors_dt
)
```

The function's algorithm has removed the *Weight* predictor: 
```{r}
low_collinearity_lst$predictors
```

