---
title: "Demo for RregressPkg::ols_calc"
author: "Rick Dean"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
library(here)

current_dir <- here::here()
data_dir <- file.path(current_dir, "demos/data")
```


## Multiple Regression College GPA: colGPA ~ hsGPA + ACT + skipped

 colGPA College GPA;  hsGPA: High School GPA;  ACT: ACT score; skipped: days skipped
 Source: "Using R for Introductory Econometrics" by Florian Heiss, page 105
 Also: "Introductory Econometrics, A Modern Approach, 6th edition" by Jeffery Wooldridge, page 115
 
### Set up the data
```{r}
data("gpa1", package = "wooldridge")
gpa1_df <- data.frame(
  colGPA = gpa1$colGPA,
  hsGPA = gpa1$hsGPA,
  ACT = gpa1$ACT,
  skipped = gpa1$skipped
)
```
### Run `RregressPkg::ols_calc()`
```{r}
gpa1_ols_ls <- RregressPkg::ols_calc(
  df = gpa1_df,
  formula_obj = colGPA ~ hsGPA + ACT + skipped
)
```

### Show the coefficient data frame
```{r}
RplotterPkg::create_table(
  x = gpa1_ols_ls$coef_df,
  caption = "MLR for colGPA ~ hsGPA + ACT + skipped"
)
```

### Show sum of the squares
```{r}
RplotterPkg::create_table(
  x = gpa1_ols_ls$anova_df,
  caption = "SS: colGPA ~ hsGPA + ACT + skipped"
)
```

## Multiple Regression Blood Pressure: BP ~ age + weight + bsa + dur + pulse + stress

Check correlations among all variables - predictors and response
Source: PennState Stat 501 Eberly College of Science, Section 12.1, Example 12.1

### Set up the data
```{r}
data_path <- file.path(data_dir, "bloodpress.txt")
bloodpress_dt <- data.table::fread(data_path)
bloodpress_dt <- bloodpress_dt[, !c("Pt")]
```

### Run `RregressPkg::ols_calc()`
```{r}
bloodpress_ols_ls <- RregressPkg::ols_calc(
  df = bloodpress_dt,
  formula_obj = BP ~ Age + Weight + BSA + Dur + Pulse + Stress
)
```

### Show the correlations among the variables
```{r}
RplotterPkg::create_table(
  x = bloodpress_ols_ls$corr_df,
  caption = "BP ~ Age + Weight + BSA + Dur + Pulse + Stress"
)
```





