---
title: "Demo for RregressPkg::ols_calc()"
author: "Rick Dean"
date: "2/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
library(here)

current_dir <- here::here()
data_dir <- file.path(current_dir, "demos/data")
```


## Multiple Regression -- College GPA 

LM Formula: colGPA ~ hsGPA + ACT + skipped
 
Source: "Using R for Introductory Econometrics" by Florian Heiss, Section 4.1 page 105
 
Also: "Introductory Econometrics, A Modern Approach, 6th edition" by Jeffery Wooldridge, Section 4.2 page 115
 
### Set up the data
```{r}
data("gpa1", package = "wooldridge")

gpa1_dt <- data.table::setDT(gpa1)
gpa1_dt <- gpa1_dt[, .(colGPA, hsGPA, ACT, skipped)]
```
### Run `RregressPkg::ols_calc()`
```{r}
gpa1_ols_ls <- RregressPkg::ols_calc(
  df = gpa1_dt,
  formula_obj = colGPA ~ hsGPA + ACT + skipped
)
```

### Show the coefficient data frame
```{r}
RplotterPkg::create_table(
  x = gpa1_ols_ls$coef_df,
  caption = "MLR for colGPA ~ hsGPA + ACT + skipped"
)
```

### Show the F statistic
```{r}
RplotterPkg::create_table(
  x = gpa1_ols_ls$F_df,
  caption = "F-statistic for colGPA ~ hsGPA + ACT + skipped",
  full_width = T,
  align_v = c("l","c","c","c","c")
)
```


### Run stats::lm() for comparison
```{r}
gpa1_lm <- stats::lm(colGPA ~ hsGPA + ACT + skipped, data = gpa1_dt)
summary(gpa1_lm)
```

### Show sum of the squares
```{r}
RplotterPkg::create_table(
  x = gpa1_ols_ls$anova_df,
  caption = "SS: colGPA ~ hsGPA + ACT + skipped",
  full_width = T,
  align_v = c("l","c","c","c")
)
```

## Multiple Regression -- R & D Expenditures

LM Formula: log(rd) ~ log(sales) + profmarg

Source: "Using R for Introductory Econometrics" by Florian Heiss, Section 4.2 page 108

Also: "Introductory Econometrics, A Modern Approach, 6th edition" by Jeffery Wooldridge, Section 4.3 page 123

### Set up the data
```{r}
data("rdchem", package = "wooldridge")

rdchem_dt <- data.table::setDT(rdchem)
rdchem_dt <- rdchem_dt[, .(rd, sales, profmarg)]
```

### Run `RregressPkg::ols_calc()`
```{r}
rdchem_ols_ls <- RregressPkg::ols_calc(
  df = rdchem_dt,
  formula_obj = log(rd) ~ log(sales) + profmarg
)
```

### Show the coefficient data frame
```{r}
RplotterPkg::create_table(
  x = rdchem_ols_ls$coef_df,
  caption = "MLR for log(rd) ~ log(sales) + profmarg"
)
```

### Show the coefficient's confidence intervals
```{r}
RplotterPkg::create_table(
  x = rdchem_ols_ls$coef_CI_df,
  caption = "Coefficient 95% Confidence Intervals",
  full_width = T,
  align_v = c("l","c","c")
)
```



