---
title: "Demo of RregressPkg::plot_fit_residuals()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```


```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
library(gamair)
```

## An example from "Introductory Econometrics"

The following example is from the text "Introductory Econometrics" Section 8-3 page 250 by Jeffrey Wooldridge.  From a Breusch-Pagan Test for heteroskedasticity, the example rejects the null hypothesis of homoskedasticity.

### Set up the data
```{r}
data("hprice1", package = "wooldridge")
hprice1_dt <- data.table::setDT(hprice1)
hprice1_dt <- hprice1_dt[,.(price, lotsize, sqrft, bdrms)]
```

### Define the OLS model formuula object
```{r}
formula_obj <-  price ~ lotsize + sqrft + bdrms
```

### Plot the fit versus the residuals
```{r, fig.width=12, fig.height=8}
RregressPkg::plot_fit_residuals(
  df = hprice1_dt,
  formula_obj = formula_obj,
  label_threshold = 100,
  label_sd = 1.0
)
```

### Re-plot after using the log of the response variable.

The text indicates that by taking the logarithmic form of the response/predictor variables, the heteroskedasticity is reduced. 

```{r, fig.width=12, fig.height=8}
formula_obj <-  log(price) ~ log(lotsize) + log(sqrft) + bdrms
RregressPkg::plot_fit_residuals(
  df = hprice1_dt,
  formula_obj = formula_obj,
  label_threshold = 0.4,
  label_sd = 1.0
)
```

## An example from "Generalized Additive Models"
The following example is from the text "Generalized Additive Models", Section 1.5, page 22  by Simon Wood.

### Set up the data
```{r}
data("sperm.comp1", package = "gamair")
sperm1_dt <- data.table::setDT(sperm.comp1)
data.table::setnames(sperm1_dt,c("time.ipc","prop.partner"), c("time_ipc","prop_partner"))
```

### Define the OLS model formula object
```{r}
formula_obj <- count ~ time_ipc + prop_partner
```

### Plot the fit versus the residuals
```{r, fig.width=12, fig.height=8}
RregressPkg::plot_fit_residuals(
  df = sperm1_dt,
  formula_obj = formula_obj,
  label_threshold = 150,
  pts_size = 2.5,
  pts_fill = "green",
  pts_color = "black"
)
```

### Plot the fit versus the square root of the standardized residuals
```{r, fig.width=12, fig.height=8}
RregressPkg::plot_fit_residuals(
  df = sperm1_dt,
  formula_obj = formula_obj,
  residual_standardized = TRUE,
  label_threshold = 1.0,
  pts_size = 2.5,
  pts_fill = "green",
  pts_color = "black"
)
```

