---
title: "Demo of RregressPkg::plot_fit_residuals()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```


```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
```

## An example plot

The following example is from the text "Introductory Econometrics" Section 8-3 page 250 by Jeffrey Wooldridge.  From a Breusch-Pagan Test for heteroskedasticity, the example rejects the null hypothesis of homoskedasticity.

### Set up the data
```{r}
data("hprice1", package = "wooldridge")
hprice1_dt <- data.table::setDT(hprice1)
hprice1_dt <- hprice1_dt[,.(price, lotsize, sqrft, bdrms)]
```

### Define the OLS model formuula object
```{r}
formula_obj <-  price ~ lotsize + sqrft + bdrms
```

### Plot the fit versus the residuals
```{r, fig.width=12, fig.height=8}
RregressPkg::plot_fit_residuals(
  df = hprice1_dt,
  formula_obj = formula_obj,
  label_threshold = 100
)
```

### Re-plot after using the log of the response variable.

The text indicates that by taking the logarithmic form of the response/predictor variables, the heteroskedasticity is reduced. 

```{r, fig.width=12, fig.height=8}
formula_obj <-  log(price) ~ log(lotsize) + log(sqrft) + bdrms
RregressPkg::plot_fit_residuals(
  df = hprice1_dt,
  formula_obj = formula_obj,
  label_threshold = 0.4
)
```


