---
title: "Demo of RregressPkg::plot_influence()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
library(here)

current_dir <- here::here()
data_dir <- file.path(current_dir, "demos/data")
```

## Single/Simple Linear Regression
Source of the data: PennState Science (https://online.stat.psu.edu/stat501/lesson/11/11.4)
Example 11-2 Revisited

### Set up the data
```{r}
data_path <- file.path(data_dir, "influence2.txt")
influence2_data_dt <- data.table::fread(data_path)
influence2_x_y_dt <- influence2_data_dt[, .(x, y)]
influence2_x_y_dt[, id := lapply(1:nrow(influence2_data_dt), function(i){paste0("ob_",i)})]
```

### Compute and plot the internal studentized residual
```{r, fig.width=12, fig.height=8}
internal_studentized_lst <- RregressPkg::plot_influence(
  df = influence2_x_y_dt,
  formula_obj = y ~ x,
  id_col = "id",
  influence_meas = "internal",
  label_threshold = 3.00,
  title = "Internal Studentized Influence Measure",
  subtitle = "Obs 21 internal studentized residual = 3.68; Source: PennState Science",
  rot_y_tic_label = T
)
internal_studentized_lst$plot
```

Observation 21 has an internal studentized residual of 3.68 and is labeled on the plot.

### Compute and plot the external studentized residual
```{r, fig.width=12, fig.height=8}
external_studentized_lst <- RregressPkg::plot_influence(
  df = influence2_x_y_dt,
  formula_obj = y ~ x,
  id_col = "id",
  influence_meas = "external",
  label_threshold = 3.00,
  title = "External Studentized Influence Measure",
  subtitle = "Obs 21 external studentized residual = 6.69; Source: PennState Science",
  rot_y_tic_label = T
)
external_studentized_lst$plot
```

Observation 21 has a external studentized residual of 6.69 and is labeled on the plot.

### Compute and plot Cook's Distance
```{r, fig.width=12, fig.height=8}
cook_lst <- RregressPkg::plot_influence(
  df = influence2_x_y_dt,
  formula_obj = y ~ x,
  id_col = "id",
  influence_meas = "cook",
  label_threshold = 0.30,
  title = "Cook's Distance Influence Measure",
  subtitle = "Obs 21 Cook's Distance = 0.36; Source: PennState Science",
  rot_y_tic_label = T
)
cook_lst$plot
```

Observation 21 has a Cook's Distance influence of 0.36 and is labeled on the plot.

## Multiple linear regression

Source of the data: "Introductory Econometrics" by Jeffrey Wooldridge, Section 9-5, page 297

### Set up the data
```{r}
data("rdchem",package = "wooldridge")
rdchem_dt <- data.table::setDT(rdchem)
rdchem_dt <- rdchem_dt[, .(rdintens, sales, profmarg)]
```

### Compute and plot Cook's Distance
```{r, fig.width=12, fig.height=8}
formula_obj <- rdintens ~ sales + profmarg
rdchem_influence_lst <- RregressPkg::plot_influence(
  df = rdchem_dt,
  formula_obj = formula_obj,
  influence_meas = "cook",
  label_threshold = 3.0,
  title = "Cook's Distance for Data Point Influence",
  subtitle = "Source: Wooldridge::rdchem",
  rot_y_tic_label = T
)
rdchem_influence_lst$plot
```

Observation 10 has a Cook's Distance influence of 3.13 and is labeled on the plot.

