---
title: "Demo of RregressPkg::plot_predictor()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RplotterPkg)
library(RregressPkg)
library(ggplot2)
library(wooldridge)
```



## Effect of *rooms* on house price

The source for the data is from "Using R for Introductory Econometrics" by Forian Heiss, Section 6.2.3, page 133.

### Show the effect of predictor *rooms* on house price

1. Set up the data:
```{r}
data("hprice2", package = "wooldridge")

hprice2_dt <- data.table::setDT(hprice2)
hprice2_dt <- hprice2_dt[, .(price, nox, dist, rooms, stratio)]
```

2. Define the OLS model:
```{r}
formula_obj <- log(price) ~ log(nox) + log(dist) + rooms + I(rooms^2) + stratio
```

3. Set five prospective values for the predictor *rooms*:
```{r}
rooms_vals_df <- data.frame(rooms = c(4,5,6,7,8))
```

4. Call `RregressPkg::plot_predictor()`:
```{r}
rooms_effect_lst <- RregressPkg::plot_predictor(
  df = hprice2_dt,
  formula_obj = formula_obj,
  predictor_vals_df = rooms_vals_df,
  title = "Influence of 'rooms' on 'log(price)'",
  subtitle = "Formula: log(price) ~ log(nox) + log(dist) + rooms + rooms^2 + stratio",
  x_title = "rooms",
  y_title = "log(price)",
  rot_y_tic_label = T
)
```

5. Plot the effect of *rooms* on *log(price)*:
```{r, fig.width=12, fig.height=8}
rooms_effect_lst$effect_plot
```

6. Plot the effect for many values of *rooms*:
```{r, fig.width=12, fig.height=8}
rooms_vals_df <- data.frame(rooms = seq(4, 8, 0.1))
rooms_effect_lst <- RregressPkg::plot_predictor(
  df = hprice2_dt,
  formula_obj = formula_obj,
  predictor_vals_df = rooms_vals_df,
  title = "Influence of 'rooms' on 'log(price)'",
  subtitle = "Formula: log(price) ~ log(nox) + log(dist) + rooms + rooms^2 + stratio",
  x_title = "rooms",
  y_title = "log(price)",
  rot_y_tic_label = T
)
rooms_effect_lst$effect_plot
```

