---
title: "Demo of RregressPkg::ols_BP_test_calc()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```

```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
```

## Heteroskedasticity in Housing Price Equations

Source: "Using R for Introductory Econometrics" by Florian Heiss (page 147)
Also: "Introductory Econometrics" by jeffery Wooldridge (page 251)

### Set up the data
```{r}
data("hprice1", package = "wooldridge")
hprice1_dt <- data.table::setDT(hprice1)
hprice1_dt <- hprice1[, .(price, lotsize, sqrft, bdrms)]
```

### Define the model formula 
```{r}
formula_obj <- price ~ lotsize + sqrft + bdrms
```

### Plot the model residuals 
```{r, fig.width=12, fig.height=12}
RregressPkg::plot_residuals_check(
  df = hprice1_dt,
  formula_obj = formula_obj,
  residual_label_threshold = 150.0,
  leverage_label_threshold = 30.0,
  title = "Housing Price Model Residuals"
)
```

### Run Breusch-Pagan Test for Heteroskedasticity
```{r}
BP_test_df <- RregressPkg::ols_BP_test_calc(
  df = hprice1_dt,
  formula_obj = formula_obj
)
RplotterPkg::create_table(
  x = BP_test_df,
  caption = "BP Test Housing Price Residuals"
)
```

The $p-values$ indicate strong evidence against the null hypothesis of homoskedasticity of variance. The square of the estimated error term is a function of the predictor coefficients.

## Logarithmic functional form of the formula object
Chapter 6 of "Introductory Econometrics" suggest a reduction of heteroskedasticity by using the logarithmic functional form.

### Define the model formula 
```{r}
log_formula_obj <- log(price) ~ log(lotsize) + log(sqrft) + bdrms
```

### Plot the model residuals 
```{r, fig.width=12, fig.height=12}
RregressPkg::plot_residuals_check(
  df = hprice1_dt,
  formula_obj = log_formula_obj,
  residual_label_threshold = 0.4,
  leverage_label_threshold = 0.15,
  title = "Log Housing Price Model Residuals"
)
```

### Run Breusch-Pagan Test for Heteroskedasticity
```{r}
BP_test_df <- RregressPkg::ols_BP_test_calc(
  df = hprice1_dt,
  formula_obj = log_formula_obj
)
RplotterPkg::create_table(
  x = BP_test_df,
  caption = "BP Test Log Housing Price Residuals"
)
```

Based on the $p-values$ we fail to reject the null hypothesis where the square of the estimated error term is not a function of the predictor coefficients.




