---
title: "Demo for RegressPkg::ols_predict_calc()"
output: 
   html_document:
    toc: yes
    toc_depth: 3
params:
  date: !r Sys.Date()    
---

```{r,setup, include=FALSE, eval=TRUE}
options(knitr.table.format = "html", width = 140)
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 12, fig.height = 8)
```


```{r, warning=FALSE, message=FALSE}
library(knitr)
library(kableExtra)
library(data.table)
library(RregressPkg)
library(RplotterPkg)
library(wooldridge)
```

The following example concerns estimating both confidence and prediction intervals for College GPA.

The source is from "Using R for Introductory Econometrics" by Florian Heiss, Section 6.2 page 130.

Also, "Introductory Econometrics" by Jeffery Wooldridge, Section 6.4, page 186.

## Confidence intervals for predictor points

Set the *interval* argument of `RregressPkg::ols_predict_calc()` to "confidence". 

### Set up the data
```{r}
data("gpa2", package = "wooldridge")
gpa2_dt <- data.table::setDT(gpa2)
gpa2_dt <- gpa2_dt[, .(colgpa, sat, hsperc, hsize)]
```

### Define the OLS formula and set target predictor values
```{r}
formula_obj <- colgpa ~ sat + hsperc + hsize + I(hsize^2)
predictor_vals_df <- data.frame(
  sat = 1200,
  hsperc = 30,
  hsize = 5
)
```

### Call RregressPkg::ols_predict_calc()  
Using the 95% confidence interval by default.
```{r}
confidence_df <- RregressPkg::ols_predict_calc(
  df = gpa2_dt,
  formula_obj = formula_obj,
  predictor_vals_df = predictor_vals_df
)
RplotterPkg::create_table(
  x = confidence_df,
  caption = "GPA 95% Confidence Interval"
)
```

### Call RregressPkg::ols_predict_calc() for a set of predictor values
Using the 99% confidence interval.
```{r}
predictor_vals_df <- data.frame(
  sat = c(1200, 900, 1400),
  hsperc = c(30, 20, 5),
  hsize = c(5, 3, 1)
)
confidence_df <- RregressPkg::ols_predict_calc(
  df = gpa2_dt,
  formula_obj = formula_obj,
  confid_level = 0.99,
  predictor_vals_df = predictor_vals_df
)
RplotterPkg::create_table(
  x = confidence_df,
  caption = "GPA 99% Confidence Intervals"
)
```

## Prediction intervals for predictor points

### Prediction interval for one set of predictors
```{r}
formula_obj <- colgpa ~ sat + hsperc + hsize + I(hsize^2)
predictor_vals_df <- data.frame(
  sat = 1200,
  hsperc = 30,
  hsize = 5
)
prediction_df <- RregressPkg::ols_predict_calc(
  df = gpa2_dt,
  formula_obj = formula_obj,
  predictor_vals_df = predictor_vals_df,
  interval = "prediction"
)
RplotterPkg::create_table(
  x = prediction_df,
  caption = "GPA 95% Prediction Interval"
)
```

### Call RregressPkg::ols_predict_calc() for a set of predictor values
Using the 95% confidence level by default. 
```{r}
formula_obj <- colgpa ~ sat + hsperc + hsize + I(hsize^2)
predictor_vals_df <- data.frame(
  sat = c(1200, 900, 1400),
  hsperc = c(30, 20, 5),
  hsize = c(5, 3, 1)
)
prediction_df <- RregressPkg::ols_predict_calc(
  df = gpa2_dt,
  formula_obj = formula_obj,
  interval = "prediction",
  predictor_vals_df = predictor_vals_df
)
RplotterPkg::create_table(
  x = prediction_df,
  caption = "GPA 95% Prediction Intervals"
)
```
